---
title: "course_project_part2.rmd"
author: "Olga Sentemova"
date: "22 Feb 2015"
output: pdf_document
---

Dataset ToothGrowth contains 60 observation of 3 variables: length of teeth, supplement method (factor with 2 levels "OJ" and "VC") and dose of vitamin C with 3 meanings.

```{r}
library(ggplot2)
library(datasets)
str(ToothGrowth)
```
```{r}
summary(ToothGrowth)
```
Lets plot our data for each of methods.

```{r}
ggplot(data=ToothGrowth, aes(x=as.factor(dose), y=len)) + 
  geom_bar(stat="identity",position=position_dodge()) +
    facet_grid(. ~ supp) +
    xlab("Dose") +
    ylab("Length")
```

Trying to investigate if supplement method affects on lenght of tooth. For this purpose we will use t-tests. 
```{r}
t.test(ToothGrowth$len[ToothGrowth$supp=="VC"], ToothGrowth$len[ToothGrowth$supp=="OJ"], 
       paired = FALSE, var.equal = FALSE)
```

As we can see we cant accept this hypothesis based on this test. So we should create 2-sample t-test.

```{r}
t.test(ToothGrowth$len[ToothGrowth$dose==0.5], ToothGrowth$len[ToothGrowth$dose==1], 
       paired = FALSE, var.equal = TRUE)
```

```{r}
t.test(ToothGrowth$len[ToothGrowth$dose==0.5], ToothGrowth$len[ToothGrowth$dose==2], 
       paired = FALSE, var.equal = TRUE)
```

```{r}
t.test(ToothGrowth$len[ToothGrowth$dose==2], ToothGrowth$len[ToothGrowth$dose==1], 
       paired = FALSE, var.equal = TRUE)
```
p in this tests less than 0.05 so we can say that dose of c-vitamin has affort to length of teeth.
